---
title: "UNC Hockey"
output:
  html_document:
    theme: journal
    highlight: tango
    toc: false
    css: "styles.css"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The North Carolina Tar Heels men’s ice hockey team is the college ice hockey team at the Chapel Hill campus of the University of North Carolina. They are members of the Atlantic Coast Collegiate Hockey League (ACCHL) and compete in the American Collegiate Hockey Association (ACHA) Division II ice hockey.

<br>

## Baseline Statistics

The following are all the season aggregates for the UNC ice hockey team. There will be links to all the writeups the UNC hockey statistics team does at the bottom of the page.

```{r inclusion, include=FALSE}
library(readr)
library(tidyverse)
library(knitr)

Indivi_Stats <- read_csv("UNC Roster Individual Febuary 6.csv")
Team_Stats <- read_csv("./23-24 UNC Team Stats - Sheet1.csv")
```

```{r summary, echo=FALSE}

FOW_Total <- sum(Indivi_Stats$FOW)
FO_Total <- sum(Indivi_Stats$FO)
FOPerc <- round((FOW_Total/FO_Total)*100, digits = 2)

#summary(Indivi_Stats)
#summary(Team_Stats)
```
<br>

## FaceOffs

> Our Tar Heel Hockey Team has a faceoff percentage of: ***`r FOPerc` %***
>
>> This is the percentage of total faceoff draws that we have won

```{r graphics, echo=FALSE}
BestFOTakers <- transmute(Indivi_Stats,
                          Player,
                           FOW,
                           FO,
            FOPercentage = round((FOW/FO)*100, digits=2)) %>% 
            subset(FO>25) %>%
            arrange(desc(FOPercentage)) 

FaceOffTable <- kable(head(BestFOTakers,5))

```

### Best FaceOff Takers: 
 `r FaceOffTable`

___

<br>
 
## Power Play and Penalty Kill

```{r PPPK, echo=FALSE}
# define df for penalty stats of all games
Penalty_DF <- transmute(Team_Stats,
                        PEN,
                        PIM,
                        PIMOPP,
                        PK,
                        PENOPP,
                        PP)

# variables to store percentages you want
PKPerc <- round((sum(Penalty_DF$PK)/sum(Penalty_DF$PEN)) * 100, digits = 2)
#print(PKPerc)
PPPerc <- round((sum(Penalty_DF$PP)/sum(Penalty_DF$PENOPP)) * 100, digits = 2)
#print(PPPerc)

# store variables for html later
PKTime <- sum(Penalty_DF$PIM)
PPTime <- sum(Penalty_DF$PIMOPP)

```
The team has killed ***`r PKPerc`%*** of penalties this season.

The team has scored on ***`r PPPerc`%*** of penalties against them this season.

<br>

### Minutes Spent on PP or PK

We have spent ***`r PKTime`*** minutes on the penalty kill this season.

While we have spent ***`r PPTime`*** minutes on the power play this season.

___

<br>

## Plus/Minus Table

```{r plusminus, echo=FALSE}
PM_DF <- subset(Indivi_Stats, Pos!="Goalie") %>%
  transmute(Player,
                   Pos,
                   `Plus/Minus`) %>%
  arrange(desc(`Plus/Minus`))

PM_DF_Table <- kable(PM_DF, format = 'simple')
```

`r PM_DF_Table`

___

<br>


## Goalie Data

```{r goalie, echo=FALSE}
Goalie_DF <- subset(Indivi_Stats, Pos=="Goalie") %>% 
              transmute(Player,
                        Saves,
                        ShotsFaced,
                        GoalsAgainst = ShotsFaced-Saves,
                        GAA = GoalsAgainst/(MinutesPlayed/60),
                        MinutesPlayed)

GoalieTable <- kable(Goalie_DF)

```

`r GoalieTable`

___

<br>

## WriteUps 

<br>

- [UNC at NCSU Febuary 2nd Pass Analysis](WriteUps/NCSU Feb2/NCSUPassAnalysis.html)

___

<br><br><br>
