---
title: "UNC vs NCSU Weekend Games"
output:
  html_document: default
  pdf_document: default
date: "2024-02-05"
---


---

<br>
```{r, include=FALSE}
library(tidyverse)
library(kableExtra)
library(gridExtra)
data <- read.csv("NCSUFeb2indiv.csv")
data2 <- read.csv("NCSUFeb5indiv.csv")
teamdata <- read.csv("23-24 UNC Team Stats - Sheet1.csv")
```

# Febuary 2nd
### Game @ Invisalgin Arena

<br>

## Plus/Minus

```{r, echo=FALSE}
offense_data <- subset(data, Pos == "Forward") %>% subset(Plus.Minus != 0)
defense_data <- subset(data, Pos == "Defense") %>% subset(Plus.Minus != 0)

plusminus_off <- ggplot(offense_data, aes(x = reorder(Player, Plus.Minus), y = Plus.Minus, fill = factor(Plus.Minus > 0))) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "#7BAFD4"), labels = c("False", "True")) +
  labs(title = "Offense +/- vs NCST 2/2",
       x = "Players",
       y = "Plus-Minus", fill = "Positive +/-?") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#plusminus_off

plusminus_def <- ggplot(defense_data, aes(x = reorder(Player, Plus.Minus), y = Plus.Minus, fill = factor(Plus.Minus > 0))) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "#7BAFD4"), labels = c("False", "True")) +
  labs(title = "Defense +/- vs NCST 2/2",
       x = "Players",
       y = "Plus-Minus", fill = "Positive +/-?") +
  coord_cartesian(ylim = c(-2,2))+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#plusminus_def

combined_graphic <- grid.arrange(plusminus_off, plusminus_def, ncol=2)
```

---

<br>

# Febuary 5th
### Game @ PNC Arena


<br>

## Plus/Minus

```{r, echo=FALSE}
offense_data2 <- subset(data2, Pos == "Forward") %>% subset(Plus.Minus != 0)
defense_data2 <- subset(data2, Pos == "Defense") %>% subset(Plus.Minus != 0)

plusminus_off2 <- ggplot(offense_data2, aes(x = reorder(Player, Plus.Minus), y = Plus.Minus, fill = factor(Plus.Minus > 0))) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "#7BAFD4"), labels = c("False", "True")) +
  labs(title = "Offense +/- vs NCST 2/5",
       x = "Players",
       y = "Plus-Minus", fill = "Positive +/-?") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#plusminus_off2

plusminus_def2 <- ggplot(defense_data2, aes(x = reorder(Player, Plus.Minus), y = Plus.Minus, fill = factor(Plus.Minus > 0))) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = c("red", "#7BAFD4"), labels = c("False", "True")) +
  labs(title = "Defense +/- vs NCST 2/5",
       x = "Players",
       y = "Plus-Minus", fill = "Positive +/-?") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#plusminus_def2

combined_graphic2 <- grid.arrange(plusminus_off2, plusminus_def2, ncol=2)
```

---

<br>

# Both Games


<br>

## Plus/Minus

```{r, echo=FALSE}
merged_data <- merge(data, data2, by = "Player", all = TRUE) %>%
  transmute(Player,
            Pos = Pos.x,
            P.M = Plus.Minus.x+Plus.Minus.y
  ) %>%
  subset(P.M != 0) %>%
  arrange(desc(P.M))

PlusMinusTable <- kable(merged_data) %>% 
  footnote(general='Plus and Minus over both games against NCSU. Players are not shown if they have a plus minus of zero.') %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left")

PlusMinusTable
```

---

<br>

## Baseline Stats

<br>

```{r, echo=FALSE}
NCSUTeamDataFG <- teamdata %>% 
  subset(Opponent=='NCSU') %>%
  subset(Period=='FG')

FaceoffPercentage <- round((sum(NCSUTeamDataFG$FaceoffWins)/sum(NCSUTeamDataFG$FaceoffAttempts)*100), digits=2)
HitTotalUNC <- sum(NCSUTeamDataFG$Hits)
HitTotalNCSU <- sum(NCSUTeamDataFG$HitsOpp)
TOTotal <- sum(NCSUTeamDataFG$TOO+NCSUTeamDataFG$TON+NCSUTeamDataFG$TOD)
TOZoneTotal <- c(sum(NCSUTeamDataFG$TOO), sum(NCSUTeamDataFG$TON), sum(NCSUTeamDataFG$TOD))
ShotTotalUNC <- sum(NCSUTeamDataFG$Shots)
ShotHouseTotal <- sum(NCSUTeamDataFG$ShotsFromHouse)
ShotHousePerc <- round((ShotHouseTotal/ShotTotalUNC)*100, digits=2)
ShotTotalNCSU <- sum(NCSUTeamDataFG$Saves)
PKTotal <- round((sum(NCSUTeamDataFG$PK)/sum(NCSUTeamDataFG$PEN))*100,digits=2)
PENTotal <- round((sum(NCSUTeamDataFG$PP)/sum(NCSUTeamDataFG$PENOPP))*100,digits=2)

TODF <- data.frame(Category = c("TOO", "TON", "TOD"),
                   Frequency = TOZoneTotal)

toplot <- ggplot(TODF, aes(x = Category, y = Frequency, fill = Category)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Turnover by Zone",
       x = "Category",
       y = "Frequency") +
  theme_minimal()

toplot

```

---

<br>



```{r, echo=FALSE}
faceoff_set <- merge(data, data2, by = "Player", all = TRUE) %>%
  transmute(Player,
            Pos = Pos.x,
            FOTotal = FO.x+FO.y,
            FOWTotal = FOW.x+FOW.y,
            FOWPerc = round((FOWTotal/FOTotal)*100, digits=2)) %>% 
  arrange(desc(FOWPerc)) %>%
  subset(FOTotal > 5)

FOWTable <- kable(faceoff_set) %>% 
  footnote(general='Shows a Player and their faceoff win percentage if they took more than 5 draws this weekend.') %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = F, position = "left") %>%
  remove_column(3)

FOWTable
```

---


Our faceoff win percentage as a team this weekend was: `r FaceoffPercentage`% 

We had `r HitTotalUNC` hits and NC State had `r HitTotalNCSU`. We outhit them by 11.

Out of the `r ShotTotalUNC` shots that we had, only `r ShotHouseTotal` were from the house. that is `r ShotHousePerc`%. NC State took `r ShotTotalNCSU` shots on us.

Our penalty kill this weekend was `r PKTotal`% and our powerplay was a `r PENTotal`%, which means we scored on zero powerplays that we had.

For season aggregates go to the main page of the website.

<br><br><br>